Analysis plan

### 2023-02-01 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd

For much of this study, no particular outcome will be analyzed. For
cluster and categorization, we will use various measures of staff work
location and frequency, for example, proportion of time teleworking or
frequency of teleworking on particular days.

@@

@@

<!-- https://www.r-bloggers.com/2021/04/cluster-analysis-in-r/ -->
<!-- https://www.guru99.com/r-k-means-clustering.html -->

For cluster analysis of staff work status, the data will be transformed
so that each row is one staff person. From the raw data, the following
variables will be defined:

@@

For cluster analysis of team work status, the data will be transformed
so that each row is one team as defined by the supervisor. Supervisors
may be in multiple teams as supervisor and subordinate. From the raw
data, the following variables will be defined:

@@

<!-- [Describe your plan to handle missing data.  How will you deal with incomplete or missing data (e.g., pairwise or listwise deletion, imputation, interpolation)?] -->

@@

>>>>

For much of this study, no particular outcome will be analyzed. For
cluster and categorization, we will use various measures of staff work
location and frequency, for example, proportion of time teleworking or
frequency of teleworking on particular days. We will investigate the
relationships between these and other factors.

@@

Both data sources will be checked for duplication and deduplicated. The unique identifiers of the daily check-in data are `employee_name` and `date`. For the roster data the unique identifier is `Full.Name` and `Snapshot.Date`. The general approach to deduplication will be that categorical variables will be restructured as indicator variables taking on a one for each category associated with the duplicate. From the roster data, if the duplication is based off of `EOD.Date`, the later date will be selected along with the other variables associated with that date. There appear to be no numeric variables.

@@

For both rules-based and cluster classification of individual staff, the
daily check-in data will be transformed so that each row is one staff person. From the
raw data, the following variables will be defined:

@@

For both rules-based and cluster classification of teams, the daily check-in data will
be transformed so that each row is one team as defined by the
supervisor. Supervisors may be in multiple teams as supervisor and
subordinate. From the raw data, the following variables will be defined:

@@

Missing data from daily check in will be treated as follows:

```{r}
tbl <- tibble("Variable Name" = c(
  "date",
"SSO",
"short_id",
"dept_id",
"employee_name",
"supervisor_name",
"location",
"daily_status",
"supervisor_correction"
),
"Treatment if missing" = c(
  "Drop observation",
  "",
  "Impute from other observations of same staff",
  "Impute from other observations of same staff",
  "Drop observation",
  "Impute from other observations of same staff",
  "Label as missing",
  "Label as missing",
  "Label as missing"
)
)
```

Missing data from the roster will be treated as follows:

```{r}
tbl <- tibble("Variable Name" = c(
"Snapshot.Date",
"Department.ID",
"Employee.Job.Business.Unit.Description",
"Full.Name",
"Employee.E.Mail.Address",
"Position.Title",
"Pay.Plan",
"Occupational.Series",
"Grade",
"EOD.Date",
"Supervisor.Level",
"Supervisor.Level.Description",
"Supervisor.Display.Name",
"Supervisor.E.Mail.Address",
"Business.Line.2.Letter.Department.ID.",
"GSA.SSO",
"Agency.Subelement.Code.Description",
"GSA.Region",
"GSA.Duty.Station.Region",
"Location.City",
"Location.State",
"Duty.Station.Code",
"Employee.Job.Bargaining.Unit.Description",
"Employee.Summary.Bargaining.Unit",
"Payroll.Accounting.Code",
"Position.Number",
"Position.Category.Code",
"Position.Category.Description"
),
"Treatment if missing" = c(
  "Label as missing",
  "Label as missing",
  "Label as missing",
  "Drop observation",
  "Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing"
)
)
```

```{r}
tbl %>% 
  flextable() %>% 
  # add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
  # set_header_labels(Group = "Level of analysis") %>% 
  merge_h(part = "header") %>% 
  merge_v(j = 1) %>% 
  theme_vanilla() %>% 
  autofit()
```
<!-- [Describe your plan to handle missing data.  How will you deal with incomplete or missing data (e.g., pairwise or listwise deletion, imputation, interpolation)?] -->

@@

<!-- https://www.r-bloggers.com/2021/04/cluster-analysis-in-r/ -->

<!-- https://www.guru99.com/r-k-means-clustering.html -->
